\documentclass[../main.tex]{subfiles}

\begin{document}
\chapter*{Acknowledgement}
\addstarredchapter{Acknowledgement}
% \minitoc
% \addstarredchapter{Acknowledgement}\adjustmtc

First, I thank God for \textbf{all the people} put in my life.
They all served as an example of who to be (or not).
The good and bad experiences made me the individual I am now.

Thanks to all my teachers and professors, who showed me the beauty of transposing knowledge from one's mind to others.
You undoubtedly instigated me to keep learning new things and inspired me to have a teaching experience during my Ph.D. studies.

I thank my parents, Rosemeri and Rogerio, for their unconditional love and selflessness in supporting my choices.
Thanks for the first education and the moral compass which guides me wherever I go. Tenho orgulho de ser filho de vocês. Obrigado por tudo, sem vocês não chegaria a lugar algum. Amo muito vocês! \footnote{I'm proud of being your son. Thanks for everything; I wouldn't get anywhere if it weren't for you. I love you very much!}

I thank my wife, Evelise.
These were difficult years for both of us for diverse reasons, but knowing you were there, made things lighter.
Thank you for choosing to be with me despite all randomness imposed on our lives.
Also, thanks for your suggestions. Having someone intelligent with critical thinking by my side always comes in handy.
I love you!

I thank my supervisors, Hervé et Romain.
Thank you for accepting me as your Ph.D. student and helping me with the initial bureaucracy.
Thanks for your patience when I was overwhelmed by the possible choices.
Taking a step back does give us a clearer overall picture.
Thanks for your guidance during these years, in research and in life.
Thanks also for the opportunity of taking classes.
Your impact on my life will never be forgotten.

I thank everybody in the AUT team of CentraleSupélec IETR for the warm reception and the chats in the break room or during lunch. It was nice to be here once again.

Thanks, Paul, for the tips on academic life.
Thanks, Mélissa, for helping me understand the administrative part of teaching.
Thank you, Pierre, for the extensive discussions on the most diverse topics and the help with my visual supports used for the conferences.
Thank you, Nabil and Marie-Anne, for always being gentle and helpful. Working with you on the other side of the curtain was a pleasure.
Thanks to my fellow Ph.D. students Marina, Alexandre, Joy, Elsy, and Zhighang for the exchanges that gave me other views on life.
I wish you all well at the end of your studies.
And I also thank my other fellow Ph.D. students, now Doctors, Amanda, Xiang, and Jesse-James.
Thanks for the help in my initial steps as a Ph.D. student and all the other moments we spent talking about work, life, music, and games.

I thank my Monitoring Committee, Malek Ghanes, and Stanislav.
The discussions about publishing, academic life, and the incentive to start teaching were invaluable.

I thank all the technical and administrative personnel at CentraleSupélec. I thank you not only for helping me during the first week but also for the enrollment in conferences and courses, solving IT problems, and finally, in this big last step. Thanks, Catherine, Karine, Cecile, Sarah, Jeannine, Véronique, Ophélie, Gaëlle, and especially Gregory Cadeau and Myriam Andrieux.

I also thank Professors Éric Bideaux, J.M. Maestre, and Ionela Prodan for accepting to be the examiners of my work.
The comments on the reports and during the defense about this work were heartwarming. The questions and discussions were inspiring.
\\~\\
And I thank you, reader, for your time. This is the work of 3 years of my life.

Enjoy.
\vfill
\end{document}
